\documentclass[a4paper,man,natbib,floatsintext,import]{apa6}
\usepackage{longtable}

\title{Analogical Transfer in a Hebb Repetition Paradigm}
\author{Oesch Adrian}
\affiliation{University of Zurich}

\begin{document}
\section{Appendix}
\subsection{Material Experiment 1}


\begin{itemize}
\item Analog Stories:
\scriptsize
\begin{longtable}{p{.08\textwidth}p{.5\textwidth}p{.42\textwidth}}
\textbf{Title} & \textbf{Statement} &\textbf{Relation-Options}\\
Bacteria & Bacteria \#1 emits enzyme \#2. & emits / expels / injects \\   & Enzyme \#2 dissolves the membrane of organ \#3. & dissolves sth. of / disintegrates sth. of / disjoints sth. of \\   & Organ \#3 fails. & fails / dies / is eliminated \\  & & \\ Crusader & Crusader group \#1 buys weapon \#2. & buys / acquires / catches \\   & Weapon \#2 breaches the fortification of town \#3. & breaches sth. of / breaks sth. of / passes sth. of \\   & Town \#3 is invaded. & is invaded / is intruded / is infiltrated \\  & & \\ Hacker & Hacker \#1 writes computer code \#2. & writes / invents / thinks of \\   & Code \#2 cracks the firewall of company \#3. & cracks sth. of / penetrates sth. of / catches sth. of \\   & Company \#3 suffers a data loss. & suffers sth. / leaks sth. / tolerates sth. \\  & & \\ Lawyer & Lawyer \#1 finds loophole \#2. & finds / detects / meets \\   & Loophole \#2 bypasses contract of union \#3. & bypasses sth. of / overrides sth. of / bystands sth. of \\   & Union \#3 loses a lawsuit. & loses sth. / forfeits sth. / files sth. \\  & & \\ Robber & Criminal \#1 learns about security issue \#2. & learns about / finds out about / starts looking \\   & Security issue \#2 suspends alarm system of museum \#3. & suspends sth. of / disrupts sth. of / inspects sth. of \\   & Museum \#3 gets robbed. & gets robbed / endures loss / is hijacked \\  & & \\ Fox & Fox \#1 digs tunnel \#2. & digs / burrow / wants \\   & Tunnel \#2 leads to coop of chicken \#3. & leads to sth. of / gets to sth. of / goes on sth. of \\   & Chicken \#3 is devoured. & is devoured / is eaten / is missing \\  & & \\
\end{longtable}
\item \normalsize Filler Stories:
\scriptsize
\begin{longtable}{p{.08\textwidth}p{.5\textwidth}p{.42\textwidth}}
Storm & Storm \#1 hits tree \#2. & hits / blows off / runs over \\   & Tree \#2 falls on trail of route \#3. & falls on / drops on / is thrown on \\   & Route \#3 is blocked. & is blocked / is jammed / is ruined \\  & & \\ Farm & Farmer \#1 purchases machine \#2. & purchases / buys / borrows \\   & Machine \#2 can collect fruit of plant \#3. & can collect / garners / can compose \\   & Plant \#3 are harvested automatically. & are harvested automatically / are reaped mechanically / are picked manually \\  & & \\ Mining & Mining company \#1 has a lot of resource \#2. & has a lot of / is filled with / fills in for \\   & Resource \#2 is sparse in country \#3. & is sparse in / is rarely found in / is sparked through \\   & Country \#3 starts negotiating. & starts negotiating / starts brokering / starts trading \\  & & \\ Pump & Plumber \#1 installs pump \#2. & installs / builds / fixes \\   & Pump \#2 sucks water from ground \#3. & sucks sth. from / transports sth. from / elevates sth. from \\   & Ground \#3 dries up. & dries up / dehydrates / soakes up \\  & & \\ Employee & Employee \#1 is assigned to project \#2. & is assigned to / is referred to / is arranged to \\   & Project \#2 supports agenda of manager \#3. & supports sth. of / emphasizes sth. of / destroys sth. of \\   & Manager \#3 gets a promotion. & gets a promotion / gets an advancement / gets a bonus \\  & & \\ Neighbor & Man \#1 takes care of cat \#2. & takes care of / looks after / is feeding \\   & Cat \#2 walks over the flowers of neighbor \#3 & walks over sth. of / goes over sth. of / strays over to \\   & Neighbor \#3 gets angry. & gets angry / becomes furious / gets aroused \\  & & \\
\end{longtable}
\end{itemize}




\end{document}
